Legends for supplementary material

### 2019-05-09 Manuscript/Figures/figure_legends.Rmd
renamed figure, referenced in manuscript
added model perfs figures with all chromosomes; editted legends

**Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution. IR was calculated by dividing the number of chromosome-specific genomic bins that overlapped with flanked TAD boundaries by the number of chromosome-specific genomic bins that did not.

**Figure 5. Comparing ensemble system specific model performances for GM12878.** Performances, separated by F1-Score and MCC, of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C). Within each predictor type, and across resolution, F1-Scores and MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).

>>>>

**Figure 4. Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution. IR was calculated by dividing the number of chromosome-specific genomic bins that overlapped with flanked TAD boundaries by the number of chromosome-specific genomic bins that did not.

**Figure 5. Comparing ensemble system specific model performances for GM12878.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C). Within each predictor type, and across resolution, MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple). Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.

### 2019-05-09 Manuscript/Supplementary/supplementary_legends.Rmd
added model perfs figures with all chromosomes; editted legends

**Supplementary Table 7. Optimal alpha and lambda penalization parameters.** The tuned alpha and lambda penalization parameter terms after performing 10-fold cross validated elastic-net regularization specific to cell line, resolution, re-sampling technique, and predictor type.

**Supplementary Figure 10. Comparing ensemble system specific model performances for K562.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C). Within each predictor type, and across resolution, F1-Scores and MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple).

>>>>

**Supplementary Figure 10. Comparing ensemble system specific model performances for K562.** Performances of random forest classification models built on each of the 3 predictor types: OC (A), OP (B), and Distance (C). Within each predictor type, and across resolution, MCCs metrics were recorded for models subsequently implemented on re-sampled data using the 4 re-sampling techniques: None (red), ROS (green), RUS (blue), and SMOTE (purple). Performances were aggregated using means across each chromosome, with error bars representing 1 standard deviation away from the mean.
